---
title: Stochastic Calculus
subtitle: Brownian Motion 
author: Victor Henriques
format: html
# bibliography: references.bib
---

# Brownian Motion

```{r}
library(ggplot2)
library(gganimate)
```

To simulate a Brownian motion sample path $W(t)$ on the interval $[0, T]$ we can adopt the following steps:

1. Choose an integer $n$ and let $\Delta = T/n$, so that $t_{i} = i\Delta t$ for $i = 0, 1,\dots,n$.

2. Generate a sequence $\varepsilon_{i},\dots,\varepsilon_{n}$ of iid standard normal rvs:

  - Generate a sequence $U_{1}, \dots, U_{n}$ of Uniform r.v.’s in the interval $(0,1)$.
  
  - Set $\varepsilon_{i} = \Phi^{-1}(x)$ where $\Phi^{-1}(x)$ is the inverse cumulative distribution of the standard Gaussian distribution.
  
  - Set $dWi = \varepsilon_{i} \sqrt{\Delta t}$.
  
3. Finally recursively construct the sample path of the BM letting:
  - $W (0) = 0$;
  - $W (t_{i}) = W (t_{i-1}) + dWi , \quad i = 1,\dots, n$
  
```{r}
# Simulate increments of the BM setting

set.seed(1)

sim = 100 # number of simulations

n = 250 # number of steps

T = 1 # Time-to-maturity

# Simulate Brownian motion process:

BM <- function(T , n, sim){
  
  dt = seq(from = 0, to = T, by = T/n) # time-step
  
  path = lapply(1:sim, function(j){
    
    Ui = runif(n = length(dt), min = 0, max = 1) # sequence of uniform rv's
    
    varepsilon = qnorm(p = Ui, mean = 0, sd = 1) # sequence of gaussian rv's
    
    dWi = varepsilon*sqrt(dt) #
    
    dW = cumsum(dWi)
    
    ts.plot(dW)
    
    return(dW)
    
    })
  
  return()
}
```
